Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/appendix.tex
edits on A.1

type qsType = ^list*$`2`int`1`->$`2`int`1`

// map : qsType -> ^list * $`2`list2`1` -> $`2`list2`1`
fun map f (l, q) = 
next {`2`
  let 
  fun m Empty2 = Empty2
    | m (Cons2(h,t)) = Cons2(prev{`1`f (l,next{`2`h`1`})`2`}, m t)
  in m prev{`1`q`2`}
`1`}

val qsMany = map qs`
\end{lstlisting}
The \texttt{map} function splits into the following two functions:
\begin{lstlisting} 
2`datatype list2 = Empty2 | Cons2 of int * list2

`1`fun map1 f = (fn (l,()) => ((), #2 (f (l, ()))), ())
`2`fun map2 (f,()) ((l,q), p : tree) =
  let 
  fun m Empty2 = Empty2
    | m (Cons2(h,t)) = Cons2(f ((l,h), p), m t) 
  in m q

`1`val (qsMany1,()) = map1 qs
`2`val qsMany2 = map2 (qs, ()) `
\end{lstlisting}

As desired, \texttt{qs1} (which is passed to \texttt{map1} via variable \texttt{f}) is executed only once per invocation of \texttt{map},
whereas \texttt{qs2} (which is passed to \texttt{map2} via variable \texttt{f}) is executed once per query.

>>>>

map : (^list * $`2`int`1` -> $`2`int`1`)
      -> ^list * $`2`list2`1` -> $`2`list2`1`
fun map f (l, q) = next {`2`
  let 
  fun m Empty2 = Empty2
    | m (Cons2(h,t)) =
                    Cons2(prev{`1`f (l,next{`2`h`1`})`2`}, m t)
  in m prev{`1`q`2`}`1`}

val mapqss = map qss`
\end{lstlisting}
The \texttt{map} function splits into the following two functions:
\begin{lstlisting} 
2`datatype list2 = Empty2 | Cons2 of int * list2

`1`fun map1 f = (fn (l,()) => ((),#2 (f (l,()))),())
`2`fun map2 (f,()) ((l,q), p : tree) =
  let 
  fun m Empty2 = Empty2
    | m (Cons2(h,t)) = Cons2(f ((l,h), p), m t) 
  in m q

`1`val (mapqss1,()) = map1 qs1
`2`val mapqss2 = map2 (qs2, ())`
\end{lstlisting}
%
Indeed, \texttt{qs1}, which is passed to \texttt{map1}, is evaluated only in the
first pass, whereas \texttt{qs2}, which is passed to \texttt{map2}, is evaluated
in the second pass, once per query \texttt{k}.
